Word Sense Disambiguation: Pipelining with Supervised LSA

### 2014-05-11 paper.tex

	\section{Introduction}
	\subsection{Problem Statement}
	  Multiple word senses

	  ex. bank: "financial institution" or "river bank" or "count on something happening" or "supply/stock held in supply for future use" ...

	  Wrong sense can drastically alter meaning

	  Objective: given context, determine which sense of the word is intended

	  First proposed by Weaver in 1949 as computational task in the early days of MT

	  One of the oldest open problems in computational linguistics

	  AI-Complete Problem

	  Example

	  "Paintings, drawings and sculpture from every period of art during the last 350 years will be on display ranging from a Tudor portrait to contemporary British art."
	  vs.
	  "Through casual meetings at cafe's, the artists drew together to form a movement in protest against the waste of war, against nationalism and against everything pompous, conventional or boring in the art of the Western world."

	  the creation of beautiful or significant things 
      vs. 
	  the products of human creativity; works of art collectively 
	\section{Literature Survey}
	knowledge based

>>>>

	\section{Introduction}
	\subsection{Problem Statement}
	Word sense disambiguation is the process of identifying the meaning of a word in its context when an individual word may take on many meanings.
	It remains one of the oldest open problems in computational lingusitics and is widely considered to be AI-Complete, 
	or as hard as the problem of making computers as intelligent as people.$^1$ Being able to accurately disambiguate word senses would greatly
	assist Machine Translation, semantic analysis, and would have significant impact in computational linguistics. However, fine-grained senses
	in which a word has multiple closely related meanings remains one of the largest challenges in word sense disambiguation. Consider the following
	example of disambiguating the sense of the word {\emph {art}} from the Senseval-2 competition held in 2001:
	\begin{enumerate}
	\item "Paintings, drawings and sculpture from every period of {\emph {art}} during the last 350 years will be on display ranging from a Tudor portrait to contemporary British art."
	\item "Through casual meetings at cafe's, the artists drew together to form a movement in protest against the waste of war, against nationalism and against everything pompous, conventional or boring in the {\emph {art}} of the Western world."
	\end{enumerate}
	In the first example, {\emph {art}} refers to {\emph {the creation of beautiful or significant things}} whereas in the second example, it refers to {\emph {the products of human creativity; works of art collectively}}. Such subtle distinctions are part of what makes word sense disambiguation a challenging problem that remains open to this day.
	\section{Literature Survey}
	knowledge based
